\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 intro.tex
minor fixes

Distributed systems are notoriously hard to design, implement and test~\cite{cavage2013there, laguna2015debugging, maddox2015test}. T
his is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with (human) clients.
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute.
A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases~\cite{gray1986computers, musuvathi2008finding}, but the consequence can be catastrophic~\cite{amazon2012aws, google2014outage}.

@@

We applied our approach to test three production distributed storage systems implemented inside Microsoft for Windows Azure cloud computing
platform---a distributed storage management system, a system for migrating data across partitions, and a big-data computing system.
We uncovered numerous bugs in these systems using our approach.
In particular, we uncovered a subtle liveness bug that was intermittently manifested during stress testing for months without being debugged.
Our testing approach uncovered this bug in a very small setting, which made it easy to examine traces, identify, and eventually fix the problem.
Our experience demonstrates that bugs in production do not need a large setting to be reproduced;
they can be reproduced in small settings with easy to understand traces.

>>>>

Distributed systems are notoriously hard to design, implement and test~\cite{cavage2013there, laguna2015debugging, maddox2015test}. This is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with (human) clients.
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute.
A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases~\cite{gray1986computers, musuvathi2008finding}, but the consequence can be catastrophic~\cite{amazon2012aws, google2014outage}.

@@

We applied our approach to test three production distributed storage systems implemented inside Microsoft for the Windows Azure cloud computing
platform: a distributed storage management system; a system for migrating data across partitions; and a big-data computing system.
We uncovered numerous bugs in these systems using our approach.
In particular, we uncovered a subtle liveness bug that was intermittently manifested during stress testing for months without being debugged.
Our testing approach uncovered this bug in a very small setting, which made it easy to examine traces, identify, and eventually fix the problem.
Our experience demonstrates that bugs in production do not need a large setting to be reproduced;
they can be reproduced in small settings with easy to understand traces.

### 2015-09-15 paper.tex
minor fixes

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today --- unit, integration, and stress testing --- are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach enables the developer to \emph{test what is being executed} and is engineered to work on production code.
It significantly improves coverage of important system behaviors and allows us to discover during testing errors that are often caught after deployment.

>>>>

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today---unit, integration, and stress testing---are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach enables the developer to \emph{test what is being executed} and is engineered to work on production code.
It significantly improves coverage of important system behaviors and allows us to discover during testing errors that are often caught after deployment.
